\huge A Usability Evaluation of Tor Launcher

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Proofread sec:quantitative.

\section{Quantitative Testing}
\label{sec:quantitative}
We performed our quantitative experiments at a behavioral laboratory many participants at a time, using instrumentation to capture evaluation metrics. We confirm prior stumbling points and user behaviors and validate our proposed design improvements.

\subsection{Recruitment}
We recruited 59 participants from the Xlab mailing list, which is a university-wide pool of participants who have opted-in to participating in social science experiments (see Appendix~\ref{quantitative-recruitment} for recruitment materials). We recruited an additional 65 participants from Craigslist to ensure diversity, since Xlab participants are primarily students and staff from UC Berkeley.

Of our 124 participants, we filtered out 10 participants who did not complete the consent form correctly or downloaded another version of Tor Browser to use during the experiment. One participant did not report their demographics, but we still used their data. Of the remaining 113, 44.2\% identified as male, 54.0\% as female, and 1.8\% as neither. They were between 18 and~68 years old ($\mu = 28.2$, $\sigma = 12.3$) and highly educated (84.1\% had at least a college education).

\subsection{Procedure}
We ran our experiment at Xlab~\cite{xlab}, an experimental social science laboratory. Xlab had 36 workstations with identical Windows~7 laptops, with workstation partitions to discourage participants from looking at other screens. At the beginning of each session, we used a script to revert the computers to a clean image, download Firefox, Chrome, Internet Explorer, VLC media player, and Tor Browser 5.0.3 (instrumented versions that logged user interactions, with/without our proposed UI changes ), set up one of the three simulated environments (E1, E2, or E3), and started recording the computer screen. We manually assigned interface--environment combinations to each computer.

We receive informed consent after talking about the study (Appendix~\ref{quantitative-script}) and instruct participants to use Tor to complete their worksheet (Appendix~\ref{summative-worksheet}), and gave them 40 minutes to complete the task. Researchers maintained minimal interactions with the participants. After the experiment and exit survey (Appendix~\ref{quantitative-exit-survey}), gave them \$30 for their time.

\subsection{Results} 
In this section, we use OLD to refer to the original interface (Figure~\ref{fig:old-interface}) and NEW to refer the version with our changes (Figure~\ref{fig:new-interface}). As seen in Table~\ref{table:participant-summary}, our design changes helped more users connect to Tor in less time. However, many, including users who used the redesigned version, still could not connect to Tor (63\% (72 of 114) of first attempts failed and 79\% (363 of 458) of total attempts failed) and those that did took long to do so (>3 minutes in E2 and >20 minutes in E3). Figure~\ref{fig:all-participant-edges} summarizes each participant--showing if they connect to Tor, how long each participant took to do so, and where they spent their time. Based on these results, we recommend that our changes be adapted in the meantime, but encourage a drastic redesign of the interface.

@@

Table~\ref{tab:attempts-bridge-proxy} shows participants' connections to Tor. As reported in the first two columns, most participants who did not need to configure anything (E1) didn't, although some optionally used a bridge. Participants who needed any bridge (E2) all used the recommended bridge. Participants who needed a meek-bridge or custom bridge (E3) chose a meek bridge at random; the ones who tried to use a custom bridge did not format their messages or inputs correctly and did not connect to Tor.

@@

Figure~\ref{fig:time_to_success_ecdf} shows a cumulative distribution of connection times. Everyone in E1 was able to connect right away; participants with the NEW interface doing so faster than participants with the OLD interface. Most participants in E2 were able to connect right away; participants with the NEW interface and OLD interface connecting in a similar distribution of time. Participants in E3 took various amount of time to succeed, with participants with the NEW interface connecting significantly faster than those with the OLD interface.

@@

Figure~\ref{fig:time_to_success_active_clamped} shows that participants' active configuration time were generally a small fraction of their connection time. E1 participants' configuration time was dominated by the time waiting for a connection to be established to Tor because they generally chose the correct configuration right away. E3 participants' configuration time was also dominated by the time waiting for a connection to be established to Tor because they usually needed to try multiple configuration options before connecting, but had to wait for the connection to time out or manually cancel their attempt between attempts. E2 participants' configuration time was a a fraction of their connection time, due to a combination of reasons that affected participants in E1 and E3.

Due to the reasons above, participants spent a majority of their time on the progress screen compared to the time spent anywhere else (Table~\ref{table:median_time}). We defined configuration time as a participant's connection time spent on all screens but the progress screen, because participants mostly waited on the progress screen. However, we noticed that some participants did utilize this time to search for help in another browser while waiting for their connection to time out, so configuration time is not a prefect metric to measure participant engagement.

>>>>

\section{Quantitative Testing}
\label{sec:quantitative}
We performed our quantitative experiments at a behavioral laboratory on many participants at a time, using instrumentation to capture evaluation metrics. We confirmed prior stumbling points and user behaviors and validated our proposed design improvements.

\subsection{Recruitment}
We recruited 59 participants from the Xlab mailing list, which is a university-wide pool of participants who have opted in to participating in social science experiments (see Appendix~\ref{quantitative-recruitment} for recruitment materials). We recruited an additional 65 participants from Craigslist to ensure diversity, since Xlab participants are primarily students and staff from UC Berkeley.

Of our 124 participants, we filtered out 10 participants who did not complete the consent form correctly or who downloaded another version of Tor Browser to use during the experiment. One participant did not report their demographics, but we still used their data. Of the remaining 113, 44.2\% identified as male, 54.0\% as female, and 1.8\% as neither. They were between 18 and~68 years old ($\mu = 28.2$, $\sigma = 12.3$) and highly educated (84.1\% had at least a college education).

\subsection{Procedure}
We ran our experiment at Xlab~\cite{xlab}, an experimental social science laboratory. Xlab had 36 workstations with identical Windows~7 laptops, with workstation partitions to discourage participants from looking at other screens. At the beginning of each session, we used a script to revert the computers to a clean image; download Firefox, Chrome, Internet Explorer, VLC media player, and Tor Browser 5.0.3 (instrumented versions that logged user interactions, with/without our proposed UI changes); set up one of the three simulated environments (E1, E2, or E3); and start recording the computer screen. We manually assigned interface--environment combinations to each computer.

We received informed consent after talking about the study (Appendix~\ref{quantitative-script}). We instructed participants to use Tor to complete their worksheet (Appendix~\ref{summative-worksheet}) and gave them 40 minutes to complete the task. Researchers maintained minimal interactions with the participants. After the experiment and exit survey (Appendix~\ref{quantitative-exit-survey}), we gave each participant \$30 for their time.

\subsection{Results} 
In this section, we use OLD to refer to the original interface (Figure~\ref{fig:old-interface}) and NEW to refer the version with our changes (Figure~\ref{fig:new-interface}). As seen in Table~\ref{table:participant-summary}, our design changes helped more users connect to Tor in less time. However, many, including users who used the redesigned version, still could not connect to Tor: 63\% (72 of 114) of first attempts failed and 79\% (363 of 458) of total attempts failed. Those that managed to connect took long to do so (>3 minutes in E2 and >20 minutes in E3). Figure~\ref{fig:all-participant-edges} summarizes each participant---showing if they connected to Tor, how long they took to do so, and where they spent their time. Based on these results, we recommend that our changes be adapted in the meantime, but encourage a drastic redesign of the interface.

@@

Table~\ref{tab:attempts-bridge-proxy} shows participants' connections to Tor. As reported in the first two columns, most participants who did not need to configure anything (E1) didn't, although some optionally used a bridge. Participants who could have used any bridge (E2) all used the recommended bridge. Participants who needed a meek bridge or custom bridge (E3) chose a meek bridge at random; the ones who tried to use a custom bridge did not format their messages or inputs correctly and failed to connect to Tor.

@@

Figure~\ref{fig:time_to_success_ecdf} shows a cumulative distribution of connection times. Everyone in E1 was able to connect right away; participants with the NEW interface doing so faster than participants with the OLD interface. Most participants in E2 were able to connect right away, with participants with the NEW interface and OLD interface taking a similar amount of time. Participants in E3 took various amount of time to succeed, with participants with the NEW interface connecting significantly faster than those with the OLD interface.

@@

Figure~\ref{fig:time_to_success_active_clamped} shows that participants' active configuration time was generally a small fraction of their connection time. The configuration time of participants in E1 was dominated by the time waiting for a connection to be established to Tor because they generally chose the correct configuration right away. The configuration time of participants in E3 was also dominated by the time waiting for a connection to be established to Tor, because they usually needed to try multiple configuration options before connecting, but had to wait for the connection to time out or manually cancel their attempt between attempts. The configuration time of participants in E2 was a modest fraction of their connection time, due to a combination of reasons that affected participants in E1 and E3.

Due to the reasons above, participants spent more time on the progress screen than on any other screen (Table~\ref{table:median_time}). We defined configuration time as a participant's connection time spent on all screens but the progress screen, because participants mostly waited on the progress screen. However, we noticed that some participants utilized this time to search for help in another browser while waiting for their connection to time out, so configuration time is not a perfect metric to measure participant engagement.
